GPU-based Adaptive Beamforming for Active Sonar Imaging

### 2012-05-07 ECUA2012/gpu_capon_ecua2012.tex
la2pdf commit - 2012:05:07	17:36:43	(Mon 7.May)

@@

>>>>

When designing an active sonar system one usually finds the image quality limited by the laterial resolution and contrast. This is a physical limitation related to the array geometry and the frequency of the transmitted signal.

@@

HUGIN: 1.8m/s - range 250m \\
fs = 100kHz*30\%*$\frac{4}{3}$ = 40kHz \\
$N_{range px} = \frac{2\,250m}{1500m/s}40kHz = 13.3kpx$ \\
$\times 32$ beams = 426kpx \\\\

PRF = $\frac{1500m/s}{2 250m} = 3Hz$ \\
TP = 215px 3Hz = 1.28Mpx/s \\
4 arrays: 1.28Mpx/s * 4 = 5.12Mpx/s
